\newpage

\section{Problem formulation}

When performing on a stage, light in the right places is important. An easy way to get that, is via controllable spotlights. They have to be able to rotate horizontally and vertically, thereby targeting specific points on the stage and do so autonomously.\\
The Pan \& Tilt System (P \& T System) can be made to meet those requirements.


\subsection{Definition of goals}
The main goals of the product is, to be able to point the cone of light from the spotlight, at a specific point on a predefined surface or follow a human walking around on a surface. The user should have the option, to specify the limits of the spotlight's working space. The positions or paths should be set by the user and the movement of the cone should be pleasant to watch.


\subsection{Requirements specification}
\label{sec:RequirementsSpecification}

The requirements will be divide into primary and secondary requirements, so as to identify the most important objectives.


\subsubsection{Primary requirements}

% Requiremnts to the hardware
\textit{Hardware requirements}

\begin{itemize}

\item The controller has to be implemented on the FPGA(Field-programmable gate array).

\item The communication between the microprocessor and the FPGA has to be done with SPI(Serial Peripheral Interface Bus).

\item The FPGA has to control the PWM(Pulse-width modulation) signal for the motors.
\end{itemize}


% Requirements to the p&t driver 
\textit{Driver requirements}
\begin{itemize}
\item The system cannot have an overshoot of more than 10\%.

\item The system has to have a settling time of at least 1.5 sec for one revolution of either pan or tilt.	

\item At a scene of dimension 5 m x 5 m, from a hight of 5 meters, the system must achieve a velocity of at least $2.5 m/s^{1}$ relative to the scene, which is the maximum velocity the average person would walk. 
\footnote{Wikipedia, Preferred walking speed, \url{https://en.wikipedia.org/wiki/Preferred_walking_speed}, 23/05/16}

\end{itemize}


% requirements to the applicaiton
\textit{Application requirements}
\begin{itemize}


\item The application must support for the spotlight to be placed at different hight

\item The application must support different stage dimensions up to 14 m x 14 m. 

\item The application must needs to be able to point its light towards a specific position on a 14 m x 14 m stage at a hight of 5 meter, with a error margin of +/- 10cm. 
\end{itemize}


\subsubsection{Secondary requirements}
These are the requirements that would be nice to have, but is not necessary for the completion of the project. 

\begin{itemize}
\item The movement between two points shall be in a smooth motion.

\item The P\&T system is to recalibrate the position of the Pan and the tilt under startup.

\item The spotlight has to be able to be controlled by an application.

\item The spotlight can be controlled by a joystick.

\item The spotlight can have a steady state close to zero
\end{itemize}
