\section{The Microcontroller}
\label{sec:TheMicrocontroller}

 Given the design requirements in section \ref{sec:RequirementsSpecification}, and the block diagram in section \ref{sec:TheSystem}. This includes all the functionality that is to be placed in the microcontroller. From here the next stage is to define the content of these blocks, and how they interact with each other. 
 
 The microcontroller is to establish an application programmer interface (API) to the P\&T driver placed in the FPGA. The microcontroller will also run the application that uses this interface in order to help the user achieve his/her goal, which is to control the spotlight.
 
 The program will be written in the C language, and it will be documented using task diagrams and state machines. 


% program structure
\input{sections/The_Microcontroller/Choice_of_Operating_System}

\input{sections/The_Microcontroller/Program_Structure}

\input{sections/The_Microcontroller/The_Application_Programmer_Interface}

\input{sections/The_Microcontroller/Event_Queues_and_Shared_State_Memory}

\input{sections/The_Microcontroller/Deadlock_Protection}

\input{sections/The_Microcontroller/SPI-Master}

\input{sections/The_Microcontroller/The_Application}

% summery 
\subsection{Overview}

The functionality of the system was meant as a fully dressed system containing all the features that would be needed while working with a real spotlight. However some of the secondary requirements cut from the final project.

\textbf{SKRIV GRUND SO DET IKKE LYDER SOM EN UNDSKYLDNING}


\textbf{The joystick:} Being able to control the spotlight via a PS2 controller is a secondary requirement. A working driver was made but the corresponding API was not. This meant that this feature was not implemented. This is not a problem as it is possible to control the system via the a PC though the UART.


\textbf{Position vs given coordinates:} The input from the P\&T system is tachs(falling and rising edges from the Hall effect sensors). This correspond to an orientation on a sphere. As the target for the spotlight is a flat surface, some conversions is needed in order to translate the desired position on the scene to an amount of tachs. The conversion takes place in \textbf{HVOR SKER DET?}.


\textbf{Following a walking person:} The system is not build with the option to change the speed, based on user input, between points. This means that rather than following a walking person, the system points at different points of the stage.


This is the functions that did not make it to the implementation

\begin{enumerate}[noitemsep]
	
	\item PS2 controller and its corresponding api
	
	\item Calculating the tack-position from the relative coordinates given by the application  
	
	

\end{enumerate}